---
title: "STAT679-III: Self-Assessment"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(MASS)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


## R Review


In this section, you will review some `R` syntax as well as simple linear regression and interpretation. If you get stuck, no problem! You can have as many re-tries as you want. Once you get the correct answer, a reference will pop up for recommended helpful link about the topic that you can read through at your convenience.


```{r quizR}
quiz(
  question("Suppose you build a simple linear model with the following code: ```mod <- lm(poverty ~ percRetail, data=mydata)```. In this example, which of the following relationships are correct:",
    answer("`poverty` is the response, `percRetail` is the predictor or explanatory variable, `mydata` is the data frame.", correct=TRUE),
    answer("`poverty` is the predictor or explanatory variable, `percRetail` is the response, `mydata` is the data frame."),
    answer("`poverty` is the response, `percRetail` is the predictor or explanatory variable, I don't know what `mydata` is."),
    incorrect="Not quite - try again! Hint: check out this [helpful link](http://www.sthda.com/english/articles/40-regression-analysis/167-simple-linear-regression-in-r/)",
    allow_retry = TRUE,
    try_again_button = "Try again.",
    correct="Correct! For more information, check out this [helpful link](http://www.sthda.com/english/articles/40-regression-analysis/167-simple-linear-regression-in-r/).")
)

```

Consider the following analysis of black cherry trees. Each tree girth (diameter), height, and volume of timber was measured for 31 felled trees. Girth measurements (diameter) are in inches. Below we show the first 6 rows of the data frame and summary of the data frame.

```{r}
data("trees")
head(trees)
summary(trees)
```

Suppose you are interested in understanding more about the relationship between tree girth (diameter) and height. You build a simple linear model:

```{r}
mod <- lm(Girth ~ Height, data=trees)
summary(mod)

stdresids <- stdres(mod)
par(mfrow = c(1,2))
plot(mod, which=1, add.smooth=FALSE); abline(h=0, lty=2, col="red")
plot(mod, which=2)
```

Using the model summary output above, fill in the blank in the interpretation of the model coefficients.

```{r quizmod}
quiz(
  question("In the above diagnostic plots, the plot on the *left* is:",
           answer("Residuals vs. fitted plot", correct=TRUE),
           answer("QQ plot"),
           answer("I'm not sure"),
           allow_retry = TRUE,
           try_again_button = "Try again.",
           incorrect = "Not quite - try again! Hint: check out this [helpful link](https://online.stat.psu.edu/stat462/node/117/)",
           correct="Correct! The plot on the left is the residuals vs. fitted diagnostic plot. For more information, check out this [helpful link](https://online.stat.psu.edu/stat462/node/117/)."),
   question("In the above diagnostic plots, the plot on the *right* is:",
           answer("Residuals vs. fitted plot"),
           answer("QQ plot", correct=TRUE),
           answer("I'm not sure"),
           allow_retry = TRUE,
           try_again_button = "Try again.",
           incorrect="Not quite - try again!  Hint: check out this [helpful link](https://data.library.virginia.edu/understanding-q-q-plots/)",
           correct="Correct! The plot on the right is the QQ plot. For more information, check out this [helpful link](https://data.library.virginia.edu/understanding-q-q-plots/)."))
```

```{r}
summary(mod)
```

```{r quizmod2}
quiz(
  question("The estimated intercept ($\\beta_0$) is:",
           answer("0.25575"),
           answer("-6.18839", correct=TRUE),
           answer("5.96020"),
           allow_retry = TRUE,
          try_again_button = "Try again",
           correct="Correct! The estimated intercept is -6.18839. For a tree with zero height, the estimated girth is -6.18839 inches.",
          incorrect="Not quite - try again!"),
  question("The estimated regression coefficient for `Height` is 0.25575 with a standard error of 0.07816. The $t$ test-statistic is:",
           answer("3.272", correct=TRUE),
           answer("0.00276"),
           answer("2.728"),
           allow_retry = TRUE,
           try_again_button = "Try again",
           correct="Correct! The $t$ test statistic is 3.272.",
           incorrect="Not quite - try again!"),
  question("The p-value of the estimated regression coefficient for `Height` is:",
           answer("0.00276", correct=TRUE),
           answer("0.2445"),
           answer("0.30722"),
           allow_retry = TRUE,
           try_again_button = "Try again",
           correct="Correct! The p-value of the estimated regression coefficient for height is 0.00276.",
           incorrect="Not quite - try again!"),
  question("For every 1 inch increase in height, we can expect a `_______` in tree girth.",
           answer("0.256 inch decrease"),
           answer("6.19 inch decrease"),
           answer("0.256 inch increase",correct=TRUE,), 
           allow_retry = TRUE,
           try_again_button = "Try again",
           correct="Correct! For every 1 inch increase in height, we can expect a 0.256 inch increase in tree girth.",
           incorrect="Not quite - try again!"),
  question("At the 0.05 level, there is `______` evidence of a relationship between tree height and girth.",
           answer("Weak"),
           answer("Strong", correct=TRUE),
           answer("No"),
           allow_retry = TRUE,
           try_again_button = "Try again. Hint: what do you use the p-value for?",
           correct="Correct! At the 0.05 level, there is strong evidence of a relationship between tree height and girth. ",
           incorrect="Not quite - try again!")
)

```


## Statistics Review


In this section, you will review some of the material from your previous statistics courses, such as t-tests, z-tests. If you get stuck, no problem! You can have as many re-tries as you want. Once you get the correct answer, a reference will pop up for recommended readings from Moore, McCabe, Craig [*Introduction to the Practice of Statistics*](https://www.amazon.com/Introduction-Practice-Statistics-Student-CD/dp/1429216220/ref=sr_1_3?dchild=1&keywords=Moore%2C+McCabe%2C+Craig+*Introduction+to+the+Practice+of+Statistics*&qid=1612931726&s=books&sr=1-3), which is also available through the University of Wisconsin-Madison [Libraries](https://search.library.wisc.edu/catalog/9910078636102121). For each question, helpful links and/or videos about the topic will also pop up once you attempt a question that you can read through at your convenience.


You may find a calculator helpful for the section below. Alternatively, you can open up a new `RStudio` session (`Session -> New Session`) and you can use the `R` console to perform the calculations.



```{r quiz}



quiz(
  question("Suppose you are exploring a random sample of 8 students from the UW-Madison campus and you are interested in learning about the average number of hours they spend listening to music. The sample mean ($\\bar{x})$) is 5, the standard deviation ($s$) is 3.63, and the sample size ($n$) is 8. Calculate the standard error.",
    answer("1.37"),
    answer("4.66"),
    answer("1.28", correct = TRUE),
    answer("0.45"),
    incorrect="Not quite - try again! Hint: check out this [helpful link](https://www.statisticshowto.com/probability-and-statistics/statistics-definitions/what-is-the-standard-error-of-a-sample/)",
    allow_retry = TRUE,
    try_again_button = "Try again.",
    correct="Correct! The standard error is $s/\\sqrt{n}=3.63/\\sqrt{8}=1.28$. For more information, please refer to Moore, McCabe, and Craig Chapter 7.1 or check out this [helpful link](https://www.statisticshowto.com/probability-and-statistics/statistics-definitions/what-is-the-standard-error-of-a-sample/)"),
  question("Following from Question 1 above, you are given that the 97.5th quantile of the $t$ distribution with 7 degrees of freedom is 2.365 (you can find this manually using this [t-distribution table](http://statcalculators.com/students-t-distribution-table/) or try using `R`: `qt(0.975, df=7)`). Calculate a 95% confidence interval for $\\bar{x}$.",
    answer("(1.96, 8.04)", correct = TRUE),
    answer("(1.76, 8.24)"),
    answer("(3.93, 6.07)"),
    answer("(-6.02, 16.02)"),
    correct="Correct! A 95% confidence interval is given by $\\bar{x}\\pm t^* \\frac{s}{\\sqrt{n}} = 5 \\pm 2.365 \\frac{3.63}{\\sqrt{8}}$. For more information, please refer to Moore, McCabe, and Craig Chapter 7.1 or check out this [helpful link](https://www.youtube.com/watch?v=gDcMG4QK-m4&feature=youtu.be)",
     incorrect="Not quite - try again! Hint: check out this [helpful link](https://www.youtube.com/watch?v=gDcMG4QK-m4&feature=youtu.be)",
    allow_retry = TRUE,
    try_again_button = "Try again"),
  question("Continuing with the example above, suppose you know that for the U.S. population, the average number of hours someone spends listening to music per day is 8.3 hours. You would like to test the hypothesis that $$H_0: \\mu = 8.3$$ vs. $$H_A: \\mu \\neq 8.3$$ Recall that from Question 1, $\\bar{x}=5$, $s=3.63$, $n=8$. Use the t-distribution to calculate the $t$ test statistics.",
  answer("-2.41"),
  answer("-2.57", correct=TRUE),
  answer("-7.27"),
  answer("3.9"),
  correct="Correct! The $t$ test statistic is given by $\\frac{\\bar{x} - \\mu_0}{s/\\sqrt{n}} = \\frac{5 - 8.3}{3.63/\\sqrt{8}} = -2.57$.  For more information, please refer to Moore, McCabe, and Craig Ch.7 or check out this [helpful link](https://www.statisticshowto.com/one-sample-t-test/)",
  incorrect="Not quite - try again! Hint: check out this [helpful link](https://www.statisticshowto.com/one-sample-t-test/)",
    allow_retry = TRUE,
    try_again_button = "Try again"),
  question("What is the p-value associated with this two-sided one-sample t-test? Hint: use the `pt()` function in `R`.",
           answer("0.0185"),
           answer("0.037", correct=TRUE),
           answer("1.96"),
           answer("0.05"),
           correct="Correct! The one-sided p-value is 0.0185 (`pt(-2.57, 7)`). However, because this is a two-sided test, we must multiply that by 2 to get 0.037 (`pt(-2.57, 7)*2`). Check out this [helpful link](https://www.socscistatistics.com/pvalues/tdistribution.aspx)",
           incorrect="Not quite - try again! Hint: check out this [helpful link](https://www.socscistatistics.com/pvalues/tdistribution.aspx).",
           allow_retry=TRUE,
           try_again_button = "Try again"),
  question("Using the evidence you found with the p-value above, at the $\\alpha = 0.05$ level, do you reject or fail to reject the null hypothesis?",
          answer("Reject $H_0$. There is moderate evidence against the null hypothesis.", correct=TRUE),
          answer("Fail to reject $H_0$. There is no evidence against the null hypothesis.", message="Not quite - try again!  Check out this [helpful link](https://online.stat.psu.edu/statprogram/reviews/statistical-concepts/hypothesis-testing/p-value-approach) or this [helpful video](https://www.khanacademy.org/math/ap-statistics/tests-significance-ap/one-sample-t-test-mean/v/comparing-p-value-from-t-statistic-to-significance-level)"),
          answer("I'm not sure", message="That's ok!  Check out this [helpful link](https://online.stat.psu.edu/statprogram/reviews/statistical-concepts/hypothesis-testing/p-value-approach) or this [helpful video](https://www.khanacademy.org/math/ap-statistics/tests-significance-ap/one-sample-t-test-mean/v/comparing-p-value-from-t-statistic-to-significance-level)"),
          correct="Correct! Check out this [helpful link](https://online.stat.psu.edu/statprogram/reviews/statistical-concepts/hypothesis-testing/p-value-approach) or this [helpful video](https://www.khanacademy.org/math/ap-statistics/tests-significance-ap/one-sample-t-test-mean/v/comparing-p-value-from-t-statistic-to-significance-level)",
          incorrect="",
          allow_retry=TRUE,
          try_again_button = "Try again")
)

```



I hope this was helpful. If you have any follow-up questions or feedback, please feel free to email me at mkamenetsky@wisc.edu.


### Helpful Links:

- [Simple Linear Regression in R](http://www.sthda.com/english/articles/40-regression-analysis/167-simple-linear-regression-in-r/)
- [Residuals vs. Fits Plot](https://online.stat.psu.edu/stat462/node/117/)
- [Understanding QQ-Plots](https://data.library.virginia.edu/understanding-q-q-plots/)
- [What is the Standard Error of a Sample](https://www.statisticshowto.com/probability-and-statistics/statistics-definitions/what-is-the-standard-error-of-a-sample/)
- [Student's t-distribution table](http://statcalculators.com/students-t-distribution-table/)
- [How to find a confidence interval with a t distribution](https://www.youtube.com/watch?v=gDcMG4QK-m4&feature=youtu.be)
- [One sample t-tests](https://www.statisticshowto.com/one-sample-t-test/)
- [P-value from TScore Calculator](https://www.socscistatistics.com/pvalues/tdistribution.aspx)
- [Hypothesis Testing (P-value approach)](https://online.stat.psu.edu/statprogram/reviews/statistical-concepts/hypothesis-testing/p-value-approach)
- [Khan Academy: Comparing P-value from t-statistic to significance level](https://www.khanacademy.org/math/ap-statistics/tests-significance-ap/one-sample-t-test-mean/v/comparing-p-value-from-t-statistic-to-significance-level)

### References:

- Statistics examples adapted from Moore, McCabe, Craig *Introduction to the Practice of Statistics*.
- Ted Laderas, [Getting LearnR tutorial to run on mybinder.org](http://laderast.github.io/2020/09/15/getting-learnr-tutorials-to-run-on-mybinder-org/)


